How to Analyze Build Logs---A~Systematic Survey and Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-08 tse-paper/content.tex
Reformat
Add approaches
Closes #50

To fill this gap, we created three novel, prototypical
implementations to
automatically analyze build logs (step \circlenum{2}).
The ideas behind the implementations are based on promising approaches
adopted from other research fields and existing build log analysis
techniques by retrieving a substring (chunk) from the build log:
\begin{itemize}
	\item \emph{Programming by Example (PBE)}, a technique
	able to
	automatically synthesize regular expressions,
	\item a technique based on information
	retrieval, which we call \emph{Common Text Similarity (CTS)},
	\item inspired by the manual ad hoc search for key parts in the
	log, a
	technique employing \emph{Keyword Search (KWS)}.
\end{itemize}

@@

In short, this article contributes
\begin{itemize}
\item the first systematic survey of the emerging field of build log
analysis.
\item three prototypical open-sourced implementations of
promising chunk retrieval techniques.
\item a large empirical study comparing the three techniques.
\item systematic guidelines on when to use which technique.
\item a detailed research map to inspire future contributions to the
field.
\item a documented replication package~\cite{brandt2020chunk-replication}.
\end{itemize}

@@

For this article, we designed and implemented three automated chunk
retrieval techniques.
Our findings of techniques in the literature
survey (~\Cref{sec:litsurresults} and \Cref{tab:litsur:techniques} in
particular) inspired the strategies that underlie them.
\Cref{tab:techniques} summarizes the techniques, which describe in detail
in the following.

@@

@@

\textbf{Comparison with more Chunk Retrieval Techniques.}
In this article, we investigated the three chunk retrieval techniques PBE,
CTS, and
KWS\@.
Our study design can be reused to evaluate other build log
analysis techniques, such as the parser Tomassi et al.
used to create
BugSwarm~\cite{tomassi2019bugswarm} or the regex-based approach
Beller et al.
used to create TravisTorrent~\cite{beller2017oops}.

>>>>

To fill this gap, we created three novel, prototypical implementations
to automatically analyze build logs (step \circlenum{2}) by retrieving a substring (chunk)
from the build log.  Our
implementations are based on the most widely used approaches
from the literature survey and as such, are meant to serve as
the ``smallest common denominator,'' with as little tuning and optimization as possible to stand protoypical for the ideas they represent:
\begin{itemize}
	\item \emph{Programming by Example (PBE)}, a technique
	able to
	automatically synthesize regular expressions,
	\item a technique based on information
	retrieval, which we call \emph{Common Text Similarity (CTS)},
	\item inspired by the manual ad hoc search for key parts in the
	log, a
	technique employing \emph{Keyword Search (KWS)}.
\end{itemize}

@@

In short, this article contributes
\begin{itemize}
\item the first systematic survey of the emerging field of build log
analysis.
\item three prototypical open-sourced implementations of
promising chunk retrieval techniques.
\item a large empirical study comparing the three techniques.
\item guidelines on when to use which technique.
\item a detailed research map to inspire future contributions to the
field.
\item a documented replication package~\cite{brandt2020chunk-replication}.
\end{itemize}

@@

For this article, we designed and implemented three automated chunk
retrieval techniques.
Our findings of techniques in the literature
survey (~\Cref{sec:litsurresults} and \Cref{tab:litsur:techniques} in
particular) inspired the strategies that underlie them.
\Cref{tab:techniques} summarizes the techniques, which we describe here in detail.

@@

Other techniques, specifically ones based on deep learning, are
thinkable, but we did not evaluate them in this article since they did
not emerge from the literature survey. Moreover, they typically
require lots of training and tuning. However, our premise was to ease
the creation of build log analysis for developers. First having to
label thousands of logs on their project before they can start to
analyze build logs is therfore infeasible. Similarly, as a manual
effort, the \emph{LogChunks} data set is not big enough to support the
training of such supervised techniques. Finding a way to train them in
an unsupervised fashion would rapidly increase their applicability and
appeal to build log analysis.

@@

\textbf{Comparison with more Chunk Retrieval Techniques.}
In this article, we investigated the three chunk retrieval techniques PBE,
CTS, and
KWS\@.
Our study design can be reused to evaluate other build log
analysis techniques, such as for example deep learning-based techniques (discussed in \Cref{sec:choice}) or manually-written programs such as the parser Tomassi et al.
created for
BugSwarm~\cite{tomassi2019bugswarm} or the regex-based approach
Beller et al.
created for TravisTorrent~\cite{beller2017oops}.
